Parsing Postfix log files

### 2007-10-23 doc/logparser.tex
Documented the EXPIRY action, including changes to the flow chart and references to the flow chart.

    \item Eventually the mail will be delivered, bounced, or deleted by the
        administrator (action: commit; flowchart:~12).  This is the last
        log line for this particular mail (though it may be indirectly
        referred to if it was re-injected).  If it is neither parent nor
        child of re-injection the data is cleaned up and entered in the
        database (flowchart:~14), then deleted from the state tables
        (flowchart:~15).  Re-injected mails are described in
        section~\refwithpage{tracking re-injected mail}.

@@

    \item If the mail is of unknown origin it is assumed to be a child mail
        whose parent hasn't yet been identified (action: commit;
        flowchart:~16).  Mark the mail as ready for entry in the database
        (flowchart:~17), and wait for the parent to deal with it
        (flowchart:~18).  The mail should not have subsequent log entries;
        only its parent should refer to it.

    \item If the mail is a child mail then it has already been tracked
        (action: commit; flowchart:~19): the data is cleaned up, missing
        data is copied from its parent if necessary, and the child is
        entered in the database (flowchart:~20), then deleted from the
        state tables (flowchart:~21).  The child mail will be removed from
        the parent mail's list of children (flowchart:~22); if this is the
        last child and the parent has also been entered in the database the
        parent will be deleted from the state tables.

    \item The last alternative is that the mail is a parent mail (action:
        commit; flowchart:~23).  Regardless of the state of its children
        the data is cleaned up and entered in the database (flowchart:~24).
        The parent may have children which are waiting to be entered in the
        database (flowchart:~25); each of those children's data is cleaned
        up and entered in the database, then deleted from the state tables.
        The parent may also have outstanding children which are not yet
        delivered, in which case (flowchart:~26) the parent must wait for
        those children to be finished with.  As soon as the last child is
        deleted from the state tables the parent will also be finished with
        (flowchart:~27), and deleted from the state tables.

@@

>>>>

    \item Eventually the mail will be delivered, bounced, or deleted by the
        administrator (action: commit; flowchart:~13).  This is the last
        log line for this particular mail (though it may be indirectly
        referred to if it was re-injected).  If it is neither parent nor
        child of re-injection the data is cleaned up and entered in the
        database (flowchart:~15), then deleted from the state tables
        (flowchart:~16).  Re-injected mails are described in
        section~\refwithpage{tracking re-injected mail}.

@@

    \item If the mail is of unknown origin it is assumed to be a child mail
        whose parent hasn't yet been identified (action: commit;
        flowchart:~17).  Mark the mail as ready for entry in the database
        (flowchart:~18), and wait for the parent to deal with it
        (flowchart:~19).  The mail should not have subsequent log entries;
        only its parent should refer to it.

    \item If the mail is a child mail then it has already been tracked
        (action: commit; flowchart:~20): the data is cleaned up, missing
        data is copied from its parent if necessary, and the child is
        entered in the database (flowchart:~21), then deleted from the
        state tables (flowchart:~22).  The child mail will be removed from
        the parent mail's list of children (flowchart:~23); if this is the
        last child and the parent has also been entered in the database the
        parent will be deleted from the state tables.

    \item The last alternative is that the mail is a parent mail (action:
        commit; flowchart:~24).  Regardless of the state of its children
        the data is cleaned up and entered in the database (flowchart:~25).
        The parent may have children which are waiting to be entered in the
        database (flowchart:~26); each of those children's data is cleaned
        up and entered in the database, then deleted from the state tables.
        The parent may also have outstanding children which are not yet
        delivered, in which case (flowchart:~27) the parent must wait for
        those children to be finished with.  As soon as the last child is
        deleted from the state tables the parent will also be finished with
        (flowchart:~28), and deleted from the state tables.

@@

    \item [EXPIRY] If Postfix has not managed to deliver a mail after
        trying for five days it will give up and return the mail to the
        sender.  When this happens the mail will not have a combination of
        Postfix programs which passes the valid combinations check (see
        section~\refwithpage{out of order log lines}).  To ensure that the
        mail can be committed the EXPIRY action sets a flag marking the
        mail as expired; the flag later causes the valid combinations check
        to be skipped, so the mail will be committed.
